Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2013-10-11 omrp.tex
Remove unneeded comments
Rewrite abstract

% Definitions of variables
\newcommand{\X}{X}
\newcommand{\x}{x} %% CHANGED THIS NOT TO BE MATHBF 
\newcommand{\xh}{{\hat{\x}}}
\newcommand{\xs}{\x^*}
\newcommand{\xit}{\xi}  %% CHANGED THIS TO BE WITHOUT TILDE! 
\newcommand{\xiti}{\xit^i}
\newcommand{\zs}{z^*}
\newcommand{\nb}{\left\lfloor\tfrac{n-m}{\gamma}\right\rfloor+1}
\newcommand{\nbl}{\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1}
\newcommand{\gammab}{\bar{\gamma}}
\newcommand{\ogb}{\tfrac{1}{\gammab}}
\newcommand{\cogb}{\left\lceil\ogb\right\rceil}

@@

% Used only for review of Meketon.  Should probably rewrite these.
%\newcommand{\xb}{\bar{x}}
%\newcommand{\xbb}{\bar{\xb}}
%\newcommand{\sx}{\{X_t, t \geq 0\}}
%\newcommand{\sxr}{\{X^n\}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\yb}{\bar{y}}
\newcommand{\ybb}{\bar{\yb}}

@@

% AUTHOR: Enter the authors of the article, see end of the example document for further examples
\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 614-292-1695. Fax:+1 614-292-7852}\\[6pt]
{\small
      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
{\small 
      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}

%% ONE WAY: JUST NAMES ON TOP, EVERYTHING ELSE AS FOOTNOTE
%\author{David~Love%
%\thanks{D.\ Love: Interdisciplinary Graduate Program in Applied Mathematics,
%University of Arizona, Tucson, AZ 85721, USA. E-mail: \texttt{dlove@math.arizona.edu}}%
%\ \ and G\"{u}zin~Bayraksan%
%\thanks{G.\ Bayraksan: (corresponding author) Department of Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA. E-mail: \texttt{guzinb@sie.arizona.edu}. Tel.: +1 520-621-2605. Fax:+1 520-621-6555}}

%%  ANOTHER WAY: ALL ON TOP, TWO DIFFERENT ONES SIDE BY SIDE
%\author{David Love \\ [6pt]
%       \texttt{dlove@math.arizona.edu} \\
%        Program in Applied Mathematics \\
%        University of Arizona \\
%        Tucson, AZ 85721, USA \\
% Multiple authors are entered as follows.
% You may also need to adjust the titlevbox size in the preamble - search for titlevboxsize
%\and
%        G\"{u}zin Bayraksan \\ [6pt]
%        \texttt{guzinb@sie.arizona.edu} \\
%        Department of Systems and Industrial Engineering \\
%        University of Arizona \\
%        Tucson, AZ 85721, USA
%}
\date{}

@@

\begin{abstract}
We investigate the use of overlapping batches for assessing solution quality in stochastic programs. 
Motivated by the original use of overlapping batches in simulation, we present a variant of the multiple replications procedure that reuses data via variably overlapping batches to obtain alternative variance estimators.  
These estimators have asymptotically lower variances, where the degree of variance reduction depends on the amount of overlap.  
We provide several desired asymptotic properties and present computational results to examine small-sample behavior.\smallskip

>>>>

% Definitions of variables
\newcommand{\X}{X}
\newcommand{\x}{x}
\newcommand{\xh}{{\hat{\x}}}
\newcommand{\xs}{\x^*}
\newcommand{\xit}{\xi}
\newcommand{\xiti}{\xit^i}
\newcommand{\zs}{z^*}
\newcommand{\nb}{\left\lfloor\tfrac{n-m}{\gamma}\right\rfloor+1}
\newcommand{\nbl}{\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1}
\newcommand{\gammab}{\bar{\gamma}}
\newcommand{\ogb}{\tfrac{1}{\gammab}}
\newcommand{\cogb}{\left\lceil\ogb\right\rceil}

@@

% Used only for review of Meketon.
\newcommand{\y}{\mathbf{y}}
\newcommand{\yb}{\bar{y}}
\newcommand{\ybb}{\bar{\yb}}

@@

\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 614-292-1695. Fax:+1 614-292-7852}\\[6pt]
{\small
      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
{\small 
      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}
\date{}

@@

\begin{abstract}
The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
Computational results for several test problems are presented, examining the small-sample behavior of the overlapping batches method.\smallskip
